\documentclass{resume} % Use the custom resume.cls style
\RequirePackage{verbatim}
\usepackage[left=0.7in,top=0.8in,right=0.7in,bottom=0.6in]{geometry} 


\begin{document}
%Headers
\def\name{Jack Davis}
\def\addressGeneral{Greater Boston Area}
\def\phone{(413) 271-4254}
\def\email{\URL{mailto:jack17davis@gmail.com}{Jack17davis@gmail.com}}
\def\github{\URL{https://github.com/jack17davis/}{github.com/jack17davis/}}
\def\linkedin{\URL{https://www.linkedin.com/in/jack17davis/}{linkedin.com/in/jack17davis/}}

%create and display header
\header{\name}{\addressGeneral}{\phone}{\email}{\linkedin}

\begin{Section}{Education}
	
	\begin{Education}{University of Massachusetts Boston}{May 2021}{Bachelor of Science in Computer Science, Minor in Mathematics}{3.7}{Honors College}
		
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
			Languages          & Java, SQL, Python, JSP, C\\
			Software \& Tools  & Git, Eclipse IDE, Bash, Vim, Linux, LaTeX, Unity \\
			Course Work       & Data Structures \& Algorithms, Linear Algebra, Probability \& Statistics, \\
			& Compilers, Databases, Artificial Intelligence, Operating Systems \\
		\end{tabular}
	\end{Education}
	
\end{Section}

\begin{Section} {Internships}
	
	\begin{Job}{Web Development Intern}{January 2020-present}{UMass Boston Computer Science Department}
		\item Maintain both front-end and back-end of \URL{http://serlwind.cs.umb.edu:8080/oats/}{tutoring website} that services the entire campus.
		\item Implement code changes and bug fixes in \textbf{Java}, \textbf{JSP}, and \textbf{SQL}.
		\item Communicate directly with our customers to provide quality service.
	\end{Job}
	
	\begin{Job}{Software Engineering Intern}{June 2020 - August 2020}{MIT Information Systems \& Technology Department}
		\item Developed, tested, and implemented best practice logging standards for 100+ \textbf{Java} applications.
		\item Investigated the possibility of using \textbf{Python} and regular expressions for automated error reporting. 
		\item Gained experience with REST APIs using \textbf{postman} and \textbf{curl}.
	\end{Job}
	
\end{Section}

\begin{Section} {Projects}
	\begin{Project} {TeXume}
		{\URL{https://github.com/jack17davis/TeXume}
			{github.com/jack17davis/TeXume/}}
		{August 2020-present}
		{LaTeX-based Resume Template}
		{Personal Project}
		\item Maintain a repository to share the \textbf{LaTeX} source code I use to generate my resume.
	\end{Project}

	\begin{Project} {PyGames}
		{\URL{https://github.com/jack17davis/PyGames}{github.com/jack17davis/PyGames/}}
		{June 2020-present}
		{library of checkers-style games}
		{Personal Project}
		\item Designing a \textbf{Python} program to play variations of checkers using artificial intelligence.
		\item Inspired by an in-course project.
	\end{Project}

\begin{comment}
	\begin{Project} {Shelley Checker}
		{\URL{https://bitbucket.org/safeiot/shelley-checker/src/master/}
		{bitbucket.org/safeiot/shelley-checker/src/master/}}
		{July 2020-present}
		{System Integration Checker}
		{Research associated with University of Massachusetts Boston}
		Helps users to plan systems and their operations, and check for possible integration errors using automata theory. I am currently adding conditional logic into the language using \textbf{Python}. 
	\end{Project}
\end{comment}
\begin{comment}
		\begin{Project}{Flex Break} {Group Project at Google JTerm Program} {January 2020}
			\item Used \textbf{Java} and \textbf{Android Studio} to create an app that allows the user to set alarms and review a list of stretches. We used \textbf{Git} to manage files.
		\end{Project}
\end{comment}
\end{Section}

\begin{Section}{Work Experience}

\begin{comment}
	\begin{Job}{Ambassador \& Peer Mentor}{September 2018-present}{UMass Boston Honors College}
			\item Create and manage the schedule for our team of six student ambassadors using \textbf{Google Sheets}.
			\item Coordinate with faculty, staff, and other ambassadors to plan and organize events for students.
			\item Meet with freshmen students both 1:1 and in groups to help them with scheduling, adjusting to college, and developing study skills.
	\end{Job}	
\end{comment}	

	\begin{Job}{Teaching Assistant}{September 2019-December 2020}{UMass Boston Computer Science Department}
			\item Facilitated \URL{https://github.com/jack17davis/cs341}{lab} for Computer Architecture and Design course for 70 students by guiding them through circuit and software construction on Arduino Uno minicomputers.
			\item Adapted course material to \URL{https://www.tinkercad.com/things/jz1DSb3UM32}{work online}, making use of hardware simulators. 
	\end{Job}
	
	
	\begin{Job}{IT Lab Consultant}{January 2019-December 2019}{UMass Boston IT Department}
		\item Maintained lab equipment, assisted students and faculty with university software, and used creative solutions to identify and troubleshoot hardware issues.
	\end{Job}
\begin{comment}
	\begin{Job}{Seafood Clerk}{June 2018-December 2018} {Shaw's Supermarkets}
		\item Consistently provided quality service to customers, assisted with inventory management.
	\end{Job}
\end{comment}
\end{Section}

\begin{Section}{Activities and Awards} \itemsep -3pt
	\begin{itemize}[leftmargin=*]
		\itemsep -0.5em %tighten up space
		\item UMass Boston 2019 Emerging Leader Award             \hfill {May 2019}
		\item UMass Boston Track and Field Team                   \hfill {Fall 2017-January 2019}
		\item Eagle Scout                                         \hfill {June 2017} 
	\end{itemize}
\end{Section}

\end{document}
